RProtoBuf: Efficient Cross-Language Data Serialization in R

### 2014-01-03 papers/rjournal/eddelbuettel-francois-stokely.Rnw
Remove Romain from authors list per his request, add an acknowledgements section which of course thanks him most of all.
Add a section on unsigned integers in the type coercion section, now
that they are handled better in RProtoBuf.

Add more text in the Descriptors subsection.

Add references to int64 (orphaned but still useful) and bit64 in the
64-bit integers subsection.



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@686 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\title{RProtoBuf: Efficient Cross-Language Data Serialization in R}
\author{by Dirk Eddelbuettel, Romain Fran\c{c}ois, and Murray Stokely}

@@

Message descriptors are represented in R with the \emph{Descriptor} S4
class. The class contains the slots \texttt{pointer} and
\texttt{type}.  Similarly to messages, the \verb|$| operator can be
used to retrieve descriptors that are contained in the descriptor, or
invoke pseudo-methods.

@@

@@

When reading the value back into R, numeric types are returned by
default, but when the full precision is required a character value
will be returned if the \texttt{RProtoBuf.int64AsString} option is set
to \texttt{TRUE}.

@@

@@

\address{Author Two\\
  Affiliation\\
  Address\\
  Country}
\email{author2@work}

>>>>

\title{RProtoBuf: Efficient Cross-Language Data Serialization in R}
\author{by Dirk Eddelbuettel and Murray Stokely}

@@

Descriptors describe the type of a Message.  This includes what fields
a message contains and what the types of those fields are.  Message
descriptors are represented in R with the \emph{Descriptor} S4
class. The class contains the slots \texttt{pointer} and
\texttt{type}.  Similarly to messages, the \verb|$| operator can be
used to retrieve descriptors that are contained in the descriptor, or
invoke pseudo-methods.

When \CRANpkg{RProtoBuf} is first loaded it calls
\texttt{readProtoFiles} to read in an example \texttt{.proto} file
included with the package.  The \texttt{tutorial.Person} descriptor
and any other descriptors defined in loaded \texttt{.proto} files are
then available on the search path.

@@

\subsection{Unsigned Integers}

R lacks a native unsigned integer type.  Values between $2^{31}$ and
$2^{32} - 1$ read from unsigned int protocol buffer fields must be
stored as doubles in R.

<<>>=
as.integer(2^31-1)
<<eval=F>>=
as.integer(2^31 - 1) + as.integer(1)
<<echo=FALSE,eval=TRUE,print=TRUE>>=
try(as.integer(2^31 - 1) + as.integer(1))

2^31
class(2^31)
@

@@

When reading the value back into R, numeric types are returned by
default, but when the full precision is required a character value
will be returned if the \texttt{RProtoBuf.int64AsString} option is set
to \texttt{TRUE}.  The character values are useful because they can
accurately be used as unique identifiers and can easily be passed to R
packages such as \CRANpkg{int64} \citep{int64} or \CRANpkg{bit64}
\citep{bit64} which represent 64-bit integers in R.

@@

\section{Acknowledgement}

\CRANpkg{RProtoBuf} was originally written in 2009 by Romain
Fran\c{c}ois and Dirk Eddelbuettel.  The authors would particularly
like to thank Romain for his initial implementation and continued
design discussions. Several features of this package are based
on the design of the \CRANpkg{rJava} package by Simon Urbanek
(dispatch on new, S4 class structures using external pointers). We'd
like to thank Simon for his indirect involvment on
\CRANpkg{RProtoBuf}.  The user defined table mechanism, implemented by
Duncan Temple Lang for the purpose of the \pkg{RObjectTables}
package allowed the dynamic symbol lookup. Many thanks to Duncan for
this amazing feature.  Kenton Varda was generous with his time in
reviewing code and explaining obscure protocol buffer semantics.  Karl
Millar and Jeroen Ooms were helpful in reviewing code or offering
suggestions.  Saptarshi Guha's contemporaneous work on \pkg{RHIPE} was a
strong motivator.

@@
